### 2019-06-12 README.Rmd
updated readme and moved to do list there

# Applying LIME to Bullet Data

Repository for research project on assessing LIME by applying it to the Hamby bullet data. The contents of this respository are listed below.

### app

@@

### code

@@

### data

@@

### journals

@@

### papers

>>>>

# LIME Research

Repository for research projects on LIME applied to the Hamby bullet data.

Link to csafe server: https://isu-csafe.stat.iastate.edu/rstudio/

## Talking points

## To Do List

**Current Week**

- look into bibText and add to paper
- work on paper
- finish journal on understanding lime (look at the RF in the local region
  lime is considering to see if it agrees with the lime explanations)
- think about how the argmin is accomplished by the LIME R package
- change distance matrix in seriation to be 5-# of variables shared between two rows
  or try using distance matrix computed on the feature values
- fix issue with seriation
- try fitting LASSO logistic model and leave one out approach (for multicollinarity)
- assess lime results on logistic regression models
- think about how to implement a simulation with a random forest
- add in feature selection methods to LIME input options
- turn repetitive code into functions
- look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
- look more into Molnar and his adviser Bernd
- Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
- he also suggested looking into SMOTE for dealing the inbalance in the classes with sampling

**Later**

- look back at 601 notes from Kaiser and Hadley's removing the blindfold and
  think about how this could be applied with random forests
- try retriculate to apply python version of lime
- look at 'removing the blindfold' for ideas
- read through Heike's new function
- think of a way to compute consistency across top two features
- compare the simple models based on different number of bins using an F-test
- look into literature on binning methods
- think about why R^2 would be better for some binning methods
- look into computing a diversity or consistency measure for the sensitivity analysis
- create distribution visualizations bins
- include a penalty for the number of parameters when choosing bins
- determine the best number of bins to use for each variable
- look at the AUC after binning
- write a draft of the examiners paper
- try out different weights
- read through LIME papers again
- compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
- try out logistic regression idea for bins (write own bin list to put in explain)
- try out subsampling idea
- read new paper on Anchor
- read book Dr. Dixon lent me on sensativity analyses
- try visualizing the features from the test data using dimension reduction and
  coloring them by variables suggested to be important by lime
- look into papers by Giles Hooker and Lucas Mentch

## Contents

Descriptions of the materials in this respository are listed below.

#### app

@@

#### code

@@

#### data

@@

#### journals

@@

#### papers
